\bf Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-03-10 notes/notes.tex
wrote width code, need to fit it

Once we have this local Hamiltonian for a particular site, we translate this over all sites \(i\), and take the average.
	\mathcal{H}_\text{full} =& \frac{1}{N}\sum_i \mathcal{H}_\text{aux}(i) = \frac{1}{N}\sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\

@@

	=& -\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{N}\sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\

@@

	\mathcal{H}_\text{full} =& -\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{2t (N-2)}{N}\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{Nw}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\

@@

				  &=-\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(\frac{2t (N-2)}{N} - \frac{2V}{Nw}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{Nw} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j 

@@

	t_{H-H} = \frac{1}{N}\left(2t (N-2) - \frac{2V}{N}\right),~ ~ U_{H-H} = \frac{1}{N}\left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{Nw}

@@

	\frac{1}{N}\sum_i \mathcal{H}_\text{aux}(i) = \mathcal{H}_{H-H}

@@

	\mathcal{G}_{H-H} = \frac{1}{\omega - \left(H_{H-H} - E_\text{gs}\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(H_\text{aux}(i) - E_\text{gs}\right)}
Rewriting eq.~\ref{siam_to_hubb} in terms of these operators, we get
	\frac{1}{N}\sum_i \left(\omega - \mathcal{G}^{-1}_\text{aux}(i)\right) = \omega - \mathcal{G}^{-1}_{H-H} \implies \frac{1}{N}\sum_i \mathcal{G}^{-1}_\text{aux}(i) = \mathcal{G}^{-1}_{H-H}~,
where we used \(\frac{1}{N}\sum_i \omega = \omega\). We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model. Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(H_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate. We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{Nw}\sum_j \sum_{k \in \text{NN of j}}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(j,k) c^\dagger_{i\sigma} | \Phi_0}

@@

	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \frac{1}{Nw} w\times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i) c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{N}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{d\sigma} | \Phi_0}

@@

	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \frac{1}{N}\sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \left(\mathcal{G}^{-1}_{H-H}\right)_{ii} = \frac{1}{N}\sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn} 

@@

	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \frac{1}{N}\sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn} 

@@

	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{i,i+1} \equiv \braket{\Phi_0 | c_{i,\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{Nw}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i,i+1) c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{Nw}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{z,\sigma} | \Phi_0}

@@

	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}

@@

	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}

@@

	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \frac{1}{N}\sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \frac{1}{N}\sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn}\\
	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}

@@

In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients. We can, therefore, use the identity
\begin{equation}\begin{aligned}
\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
\end{aligned}\end{equation}
We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions. Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as 
\begin{gather}
	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \frac{1}{N}\sum_{n} |d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \frac{1}{N}\sum_{n} |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\\
	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}_\text{aux}(d, -\omega) \right)_{nn}
\end{gather}

The Lehmann-Callen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements. Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
\begin{equation}\begin{aligned}
	\label{greens_func_siam}
	\left(G_{H-H}(\omega)\right)_\text{loc} &= \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \frac{1}{N}\sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
	\left(G_{H-H}(\omega)\right)_\text{n-n} &= \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{Nw}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] 
\end{aligned}\end{equation}

@@

			     &= \frac{1}{N}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]

@@

	&= -\frac{1}{N\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
	&= \frac{1}{N}\left [A_\text{aux,dd} + \frac{\xi_{\vec k}}{w} A_\text{aux,dz}\right]

@@

Further, \textbf{CHECK!}

@@

%= \sum_{\vec{k}}A_{H-H}(\vec{k},\omega) 
= \frac{A_\text{aux,dd}}{N}

@@

With the knowledge of the momentum-space Greens function $G_\text{H-H}(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
\begin{equation}\begin{aligned}
	\Sigma(\vec k,\omega) = G_0(\vec k,\omega)^{-1} - G(\vec k,\omega)^{-1}
\end{aligned}\end{equation}
where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system. Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
\begin{equation}\begin{aligned}
	\Sigma_{H-H}(\vec k,\omega) &= \omega +t^{H-H}\xi_{\vec k} - N\left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
&= 	 \omega +t^{H-H}\xi_{\vec k} - N\left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
\end{aligned}\end{equation}
This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.

>>>>

Once we have this local Hamiltonian for a particular site, we translate this over all sites \(i\):
	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\

@@

	=& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\

@@

	\mathcal{H}_\text{full} =& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{w}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\

@@

				  &=-\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{w}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{w} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j 

@@

	t_{H-H} = \left(2t (N-2) - \frac{2V}{N}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{w}

@@

	\sum_i \mathcal{H}_\text{aux}(i) = \mathcal{H}_{H-H}

@@

	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(H_\text{aux}(i) - E_\text{gs}\right)}
Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian, while the primed quantities \(E_\text{gs}^\prime\) and \(\omega^\prime\) are the same quantities but for the full model \(\mathcal{H}_{H-H}\). From the relation eq.~\ref{siam_to_hubb} we know that while the auxiliary model is intensive, the full Hamiltonian is extensive (scales with system size). This means that we must have \(\omega^\prime = N\omega\) and \(E_\text{gs}^\prime = N E_\text{gs}\).
Rewriting eq.~\ref{siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
\sum_i \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i)\right) = N\omega + N E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_i \mathcal{G}^{-1}_\text{aux}(i) = \mathcal{G}^{-1}_{H-H}~,
We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model. Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(H_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate. We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{w}\sum_j \sum_{k \in \text{NN of j}}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(j,k) c^\dagger_{i\sigma} | \Phi_0}

@@

	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \frac{1}{w} w\times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i) c^\dagger_{i\sigma} | \Phi_0} = \braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{d\sigma} | \Phi_0}

@@

	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \left(\mathcal{G}^{-1}_{H-H}\right)_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn} 

@@

	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn} 

@@

	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{i,i+1} \equiv \braket{\Phi_0 | c_{i,\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i,i+1) c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{z,\sigma} | \Phi_0}

@@

	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}

@@

	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}

@@

	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn}\\
	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}

@@

In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients. We can, therefore, use the identity
\begin{equation}\begin{aligned}
\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
\end{aligned}\end{equation}
We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions. Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as 
\begin{gather}
	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\\
	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}_\text{aux}(d, -\omega) \right)_{nn}
\end{gather}

The Lehmann-Callen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements. Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
\begin{equation}\begin{aligned}
	\label{greens_func_siam}
	\left(G_{H-H}(\omega)\right)_\text{loc} &= \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
	\left(G_{H-H}(\omega)\right)_\text{n-n} &= \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{w}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] 
\end{aligned}\end{equation}

@@

			     &= \sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]

@@

	&= -\frac{1}{\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
	&= A_\text{aux,dd} + \frac{\xi_{\vec k}}{w} A_\text{aux,dz}

@@

Further,

@@

= A_\text{aux,dd}

@@

With the knowledge of the momentum-space Greens function $G_\text{H-H}(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
\begin{equation}\begin{aligned}
	\Sigma(\vec k,\omega) = G_0(\vec k,\omega)^{-1} - G(\vec k,\omega)^{-1}
\end{aligned}\end{equation}
where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system. Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
\begin{equation}\begin{aligned}
	\Sigma_{H-H}(\vec k,\omega) &= \omega +t^{H-H}\xi_{\vec k} - \left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
&= 	 \omega +t^{H-H}\xi_{\vec k} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
\end{aligned}\end{equation}
This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
